A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-28 6_validation.tex
some changes in sec. 5

\section{Validation}
In order to test our framework, we have assembled a data set of different types of 3D models, ranging over various applications and various types of geometry.
The data set is described in detail in the accompanying data in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices from the total set of slices for analysis.
We generated the toolpaths on these 300 outline shapes using the uniform technique as implemented by Clipper and compare it to the 4 beading schemes discussed in \cref{sec_generalization}, namely constant bead count scheme with a bead count of $C=4$, the centered beading scheme, the evenly distributed, and the inward distributed beading scheme, using a nominal bead widths of $w^*] = \SI{0.4}{\milli\meter}$.

\subsection{Computational analysis}
Experiments were performed on an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} using a single core and \SI{16.3}{\giga\byte} memory.
The uniform width offsetting technique was implemented using the state-of-the-art polygon offset library Clipper~\cite{johnson2014clipper}.
The computation time of each slice from the data set was recorded for the uniform technique and the inward distributed scheme. 
\cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.

>>>>

\section{Validation}
We evaluate the proposed framework and the various beading schemes on a set of different types of 3D models, ranging over various applications and various types of geometry. 
The data set is described in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices for analysis.
Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library, and by our framework using four beading schemes, i.e. the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme, all with a nominal bead widths of $w^*] = \SI{0.4}{\milli\meter}$. The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.

\subsection{Computational analysis}

The computation time of each slice from the data set was recorded for the uniform technique and the inward distributed scheme. 
\cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.
